Seminarium TI 3700\\ Data Analysis on Twitter(working title)

### 2014-03-23 authorinstr_2.tex
Much Event identification, such user classification, very conclusive. Wow

The next section was again a higher level of abstraction. In this chapter we did not consider the data hidden in a single tweet, the focus was on a stream of tweets and what information can be extracted from a stream of tweets. First up was the user modelling. The idea here is that we can use the tweets from a certain user to create a profile from that user.

>>>>

The next section was again a higher level of abstraction. In this chapter we did not consider the data hidden in a single tweet, the focus was on a stream of tweets and what information can be extracted from a stream of tweets. We discussed User Classification, which can be a useful feature to gather information about people, their opinions and hobbies. These techniques can be used for predicting things people like such as their political view. We discussed the concept of event identification which can be separated in two problems (1) Separating event and non-event content and (2) Aligning Tweets with an Event. We presented solutions for these problems and shown that event identification can be a useful technique in practice. (e.g. It can be used to detect Earthquakes)
